### 2021-04-07 input/figdel.tex
figures

\begin{figure*}
  \begin{center}
    \subfloat[Part A][\label{fig:delA}Both Process $a$ and
      Process $c$ initiate then remove a partition.
      $w_{ab} = 1.5$; $w_{bc} = w_{cd} = w_{bd} = 1$.]{\input{input/figdelA.tex}}
    \hspace{5pt}
    \subfloat[Part B][\label{fig:delB}Process $b$ and Process $d$ receive and deliver
      messages based on their weights. $a$'s partition propagates to all processes.]
             {\input{input/figdelB.tex}}
    \hspace{5pt}
    \subfloat[Part C][\label{fig:delC}Process $c$'s partition reach $b$ and $d$.
      Its removal shortly follows. Process $b$ does not have any control
      information about partitions any more.]{\input{input/figdelC.tex}}
    \hspace{5pt}
    \subfloat[Part D][\label{fig:delD}Processes discard remaining messages.
      Process $b$ does not deliver $\delta_a$, for it already removed $a$ when
      Partition $c$ dominated it. Processes $c$ and $d$ remain in an incorrect
      partition.]{\input{input/figdelD.tex}}
  \end{center}
  \caption{\label{fig:del}Partition removals cannot rely only on
    current partition, for it may lead to either inconsistent
    partitioning, or every process receiving every broadcast.}
\end{figure*}

>>>>

\begin{figure}
  \begin{center}
    \subfloat[Part A][\label{fig:delA}Process~$a$ deletes its
      partition.  It notifies all processes that belong to its
      partition using \NAMEB.]{\input{input/figdelA.tex}}
    \hspace{5pt}
    %
    \subfloat[Part B][\label{fig:delB}$\delta$s stop as soon as they
      encounter another partition. Process~$b$ answers with its
      partition.]{\input{input/figdelB.tex}}
  \end{center}
  \caption{\label{fig:del}Efficient removal of a partition using
    \NAME. Process~$a$ eventually knows that it belong to Partition
    $P_c$.}
\end{figure}

### 2021-04-07 input/proposal.tex
figures

Unfortunately, processes do not share a common global knowledge of the
network state. For processes to reach consistent partitioning
together, a process becoming a source must notify every process that
is closer to it than any other source. Epidemic
dissemination~\cite{birman1999bimodal} constitutes an efficient
communication pattern to perform such operation.

@@

\begin{proof}
  \begin{asparadesc}
  \item [$BEF \implies CP$:] When a process $s_1$ becomes a source, it
    belongs to its own partition, for there exists no better partition
    than its own: $\forall p \in V: |\Pi_{s_1 s_1}| < |\Pi_{s_1
      p}|$. It broadcasts such message to its neighbors. Since
    communication channels are reliable, neighboring processes
    eventually receive such notification. In particular, whatever the
    order of received messages, every process $p_1$ such that there
    exists no better partition $s_2$ than the received one delivers
    and forwards it: $\forall s_2 \in S: |\Pi_{p s_1}| < |\Pi_{p
      s_2}|$. The notification emanating from $s_1$ transitively
    reaches all such processes through shortest paths. Since there
    exists only one best value per process that can never be
    retracted, processes eventually reach consistent
    partitioning. \TODO{Rework this with $s_{pq}$ and $r_{pq}$.}
  \item [$CP \implies BEF$:] \TODO{By contradiction, if there is a
    process $p$ that does not forward, then another process $q$ may
    never gets its best because it needs the weight $W_{pq}$.}
  \end{asparadesc}
\end{proof}

@@

Algorithm~\ref{algo:add} shows the instructions that implement such
consistent partitioning when
\begin{inparaenum}[(i)]
\item weights are scalar values,
\item processes only add new partitions to the system,
\item and processes never crash nor leave the system.
\end{inparaenum}
 Figure~\ref{fig:add} illustrates its behavior on a system comprising
 4 processes $a$, $b$, $c$, and $d$. Two processes $a$ and $c$
 concurrently create a partition by S-broadcasting their respective
 \underline{a}dd message: $\alpha_a^0$ and $\alpha_c^0$. They
 initialize their own state with the lowest possible bound $0$ (see
 Line~\ref{line:lowestbound}), and send a message to each of their
 neighbors by accumulating the corresponding edge weight (see
 Line~\ref{line:accumulator}). In Figure~\ref{fig:addC}, Process $b$
 receives $\alpha_{c}^{1}$. Since it improves its own partition
 distance, it keeps it and forwards it to its neighbors. Process $b$
 discards $\alpha_{b}^{1.5}$, for it does not improve its partition
 distance. Processes $c$ and $d$ will never hear of Process $a$'s
 partition.  In Figure~\ref{fig:addD}, processes discard last
 transiting messages. The system converged to the consistent
 partitioning. However, since processes operate using local knowledge
 only, generated traffic may be sub-optimal, for processes may
 receive, deliver, and forward messages emanating from a same source
 simply because it did not come from the shortest path yet.

@@

\subsection{Dynamic consistent partitioning}
At any time, a process can become a source, hence adding a new
partition to the system. This partition eventually includes all
processes that are closer from this new source than any other
else. Processes naturally converge towards their respective best
partition by only piggybacking a monotonically increasing distance in
forwarded messages.

Then, at any time, a source can revoke its self-appointed status of
source, hence deleting its partition from the system. All processes
that belong to this partition must eventually choose another partition
to belong to. Unfortunately, stale control information about deleted
partitions may impair the propagation of both
\begin{inparaenum}[(i)]
\item notifications about actual sources, and
\item notifications about other deleted partitions.
\end{inparaenum}
The correctness of the partitioning depends on receipt orders at each
processes.

>>>>

Unfortunately, processes do not share a common global knowledge of the
network state. For processes to reach consistent partitioning
together, a process becoming a source must notify every process that
is closer to it than any other source. Epidemic
dissemination~\cite{birman1999bimodal} constitutes an efficient
communication pattern to perform such operation. \TODO{More about
  \emph{forwarding}.}

@@

\begin{proof}
  \begin{asparadesc}
  \item [$BEF \implies CP$:] When a process $s_1$ becomes a source, it
    belongs to its own partition, for there exists no better partition
    than its own: $\forall p \in V: |\Pi_{s_1 s_1}| < |\Pi_{s_1
      p}|$. It broadcasts such message to its neighbors. Since
    communication channels are reliable, neighboring processes
    eventually receive such notification. In particular, whatever the
    order of received messages, every process $p_1$ -- such that there
    exists no better partition $s_2$ than the received one -- delivers
    and forwards it: $\forall s_2 \in S: |\Pi_{p s_1}| < |\Pi_{p
      s_2}|$. The notification emanating from $s_1$ transitively
    reaches all such processes through shortest paths. Since there
    exists only one best value per process that can never be
    retracted, processes eventually reach consistent
    partitioning. \TODO{Rework this with $s_{pq}$ and $r_{pq}$.}
  \item [$CP \implies BEF$:] \TODO{By contradiction, if there is a
    process $p$ that does not forward, then another process $q$ may
    never gets its best because it needs the weight $W_{pq}$.}
  \end{asparadesc}
\end{proof}

@@

Algorithm~\ref{algo:add} shows the instructions that implement such
consistent partitioning when
\begin{inparaenum}[(i)]
\item weights are scalar values,
\item processes only add new partitions to the system,
\item and processes never join nor crash nor leave the system.
\end{inparaenum}
 Figure~\ref{fig:add} illustrates its behavior on a system comprising
 4 processes $a$, $b$, $c$, and $d$. Two processes $a$ and $c$
 concurrently create a partition by S-broadcasting their respective
 \underline{a}dd message: $\alpha_a^0$ and $\alpha_c^0$. They
 initialize their own state with the lowest possible bound $0$ (see
 Line~\ref{line:lowestbound}), and send a message to each of their
 neighbors by accumulating the corresponding edge weight (see
 Line~\ref{line:accumulator}). In Figure~\ref{fig:addC}, Process $b$
 receives $\alpha_{c}^{1}$. Since it improves its own partition
 distance, it keeps it and forwards it to its neighbors. Process $b$
 discards $\alpha_{b}^{1.5}$, for it does not improve its partition
 distance. Processes $c$ and $d$ will never hear of Process $a$'s
 partition.  In Figure~\ref{fig:addD}, processes discard last
 transiting messages. The system converged to the consistent
 partitioning. However, since processes operate using local knowledge
 only, generated traffic may be sub-optimal, for processes may
 receive, deliver, and forward messages emanating from a same source
 simply because it did not come from the shortest path yet.

@@

\subsection{Dynamic consistent partitioning}

At any time, a process can become a source, hence adding a new
partition to the system. This partition eventually includes all
processes that are closer from this new source than any other
else. Processes naturally converge towards their respective best
partition by only piggybacking a monotonically increasing distance in
forwarded messages.

Then, at any time, a source can revoke its self-appointed status of
source, hence deleting its partition from the system. All processes
that belong to this partition must eventually choose another partition
to belong to. In Figure~\ref{fig:del}, two partitions exist initially:
$P_a$ and $P_c$ that respectively include $\{a\}$, and $\{b, c,
d\}$. In Figure~\ref{fig:delA}, Process $a$ deletes its partition. It
notifies all neighboring processes -- here only Process $b$ -- that
may belong to its partition using \NAMEB. Upon receipt, Process $b$
discards the message $\delta_a$, for the latter does not target the
former's partition. Yet, Process $b$ sends its own partition that may
be the best for Process $a$. Eventually, every processes belong to the
same partition $P_c$.

\input{input/figdel.tex}

Unfortunately, stale control information about deleted partitions may
impair the propagation of both
\begin{inparaenum}[(i)]
\item notifications about actual sources, and
\item notifications about other deleted partitions.
\end{inparaenum}
\TODO{Figure showing inconsistency.}
The correctness of the partitioning depends on receipt orders at each
processes.

\input{input/figproblem.tex}
